### 2023-07-11 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny

Under a linear shear flow, a multicomponent vesicle exhibits more exotic dynamics in both shape and membrane composition \cite{Sohn2010_JCP, Smith2007_JChemPhys,Cox2015_Nonlinearity,Liu2017_SoftMatter,Gera2018_SoftMatter,Gera2022_JFM} than a single-component vesicle.
For example, multicomponent vesicles under a background flow often exhibit highly complex morphologies, leading to vesicle budding. 
The hydrodynamics of these
multicomponent vesicles include phase treading, tumbling with no
viscosity contrast, swinging, budding, and
fission~\cite{soh-tse-li-voi-low2010, wan-du2008, all-ama2006,
ger-sal-spa2022, lip1992, urs-klu-phi2009}. In addition to the
aforementioned numerical studies, these dynamics have been observed in
experiments~\cite{bag-sun2009, yan-ima-tan2010, yan-ima-tan2008,
dre-jah-bob-spa-gop2021}.

>>>>

Under a linear shear flow, a multicomponent vesicle exhibits more exotic dynamics in both shape and membrane composition \cite{Sohn2010_JCP, Smith2007_JChemPhys,Cox2015_Nonlinearity,Liu2017_SoftMatter,Tusch2018_PRF,Gera2018_SoftMatter,Gera2022_JFM} than a single-component vesicle.
For example, multicomponent vesicles under a background flow often exhibit highly complex morphologies, leading to vesicle budding. 
The hydrodynamics of these
multicomponent vesicles include phase treading, tumbling with no
viscosity contrast, swinging, budding, and
fission~\cite{soh-tse-li-voi-low2010, wan-du2008, all-ama2006,
ger-sal-spa2022, lip1992, urs-klu-phi2009}. In addition to the
aforementioned numerical studies, these dynamics have been observed in
experiments~\cite{bag-sun2009, yan-ima-tan2010, yan-ima-tan2008,
dre-jah-bob-spa-gop2021}.
